\chapter*{Thanks to\markboth{Thanks to}{}} 
\addcontentsline{toc}{chapter}{Thanks to}
I am finally writing the last page of this thesis and I would like to spend a few words to say thanks to all the people that were with me through this journey.\\

Thanks to my family. In particular my mother, my father and my brother. You are always there for me, even when, under pressure, I tend to make myself unbearable. Your support is truly important, I would not go far without it.\\

Thanks to my love, Valentina. Well, \virgolette{I don't even need to sugarcoat it}, right? You are part of my family by now, so... read above!\\

Thanks to Andrea, maybe my supporter number one (after my mother, of course). It was a while ago, but you convinced me that I am worthy of something.\\

Thanks to all my friends. I am lucky (or lazy?) enough to say that you are too many, so I cannot write all your names. However, if even only one time, you were patient enough to listen to me talking about that line of code I had written, then... thank you, that meant a lot!\\

Thanks to Boris, my thesis co-supervisor, my teaching assistant and my classmate. You were always kind and willing to help me. I learned a lot from you.\\

Thanks to Alessandro, for the opportunity of doing this thesis and the help you always kindly provided me.\\

Thanks to Professor Pezz\`e, Professor Denaro and double degree coordinators for the opportunity of this double degree.\\

And if you, who are reading now, if you think that I forgot to thank you, then... thank you! We good, right?